\documentclass[12pt,twoside]{article}
    \usepackage{jmlda}
    %\NOREVIEWERNOTES
    \title
        {Building reference objects for a set of multidimensional time series}
    \author
        {Goncharov~A.\,V., Iskhakov~R.\,A., Korepanov~G.\,M., Solodnev~S.\,A., Samirhanov~D.\,I.} % основной список авторов, выводимый в оглавление
    \thanks{
        The work is done with generous RFBR support, project \No\,00-00-00000.
        Supervisor:  Goncharov~A.\,V.
        Problem is set by:  Goncharov~A.\,V.
        Consultant:  Goncharov~A.\,V.
    }
    \email
        {iskhakov.ra@phystech.edu, korepanov.gm@phystech.edu, solodnev.sa@phystech.edu, samirhanov.di@phystech.edu}
    \organization
        {МФТИ}

    \abstract{
    	\textbf{Abstract} - In this study we explore building reference object for time series cluster. Solving the problem of finding the best pattern (reference object), we first use DTW distance for preliminary clusterization. The research focuses on the study of methods of summarising (averaging) of different time series within one cluster using DBA algorithm.
    	
        \bigskip
        \textbf{Keywords}: \emph {time series, averaging, dynamic time warping, classification}.
    }
    
    % \titleEng
    %     {JMLDA paper example: file jmlda-example.tex}
    % \authorEng
    %     {Author~F.\,S.$^1$, CoAuthor~F.\,S.$^2$, Name~F.\,S.$^2$}
    % \organizationEng
    %     {$^1$Organization; $^2$Organization}
    % \abstractEng
    %     {This document is an example of paper prepared with \LaTeXe\
    %     typesetting system and style file \texttt{jmlda.sty}.
    
    %     \bigskip
    %     \textbf{Keywords}: \emph{keyword, keyword, more keywords}.}
        
    \begin{document}

    \maketitle
    \section{Introduction}
    \section{Section}
    \paragraph{Paragraph}
    \section{Conclusion}

    \bibliographystyle{unsrt}
    \bibliography{jmlda-bib}

    \begin{thebibliography}{1}
    \bibitem{voron06latex}
       \BibAuthor{Воронцов~К.\,В.}
       \LaTeXe\ в~примерах.
       2006.
       \BibUrl{http://www.ccas.ru/voron/latex.html}.
    \bibitem{Lvovsky03}
       \BibAuthor{Львовский~С.\,М.} Набор и вёрстка в пакете~\LaTeX.
       3-е издание.
       Москва:~МЦHМО, 2003.  448~с.
    \end{thebibliography}
    
    % Решение Программного Комитета:
    %\ACCEPTNOTE
    %\AMENDNOTE
    %\REJECTNOTE
    \end{document}
    